Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-05-09 manuscript/manuscript.tex
Added caption to grid search figure in manuscript

\begin{figure}
\centering
\includegraphics[width=\linewidth]
    {figures/grid-search.pdf}
\caption{
    }
\label{fig:grid-search}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=\linewidth]
    {figures/grid-search.pdf}
\caption{
    Numerical error exploration in the $D$, $\delta$ space.
    The percentage difference values were obtained from the comparison 
    between the analytical solution and the numerical approximation of 
    the gravitational fields ($V$, $g_z$ and $g_{zz}$) generated by a 
    spherical shell with an exponential density as the one defined on 
    equation \ref{eq:density-exp}.
    These comparison have been carried out with a spherical shell of 
    35km of thickness, whose density function has a value of $b$ of 1km 
    and the gravitational fields were computed on the big grid 
    (defined in Table \ref{tab:grids}).
    The points inside the dashed line are the ones that present an 
    error lower than 0.1\%.
    }
\label{fig:grid-search}
\end{figure}
